---
title: "Project 1"
author: "Ziyi Liao "
output: html_notebook
---

#Part 0: Clean the data
##Step 1. load the libraries 
```{r load libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidytext)
library(DT)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny) 
```
```{r other libraries, warning = FALSE, message =FALSE}
library(SnowballC)
library(wordcloud)
library(tm)
library(topicmodels)
library(RColorBrewer)
library(dplyr)
```

##Step 2: Process the data
```{r}
hm_data <- read_csv("../output/processed_moments.csv")

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read_csv(urlfile)

happydb <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))

# Merge the text data with demographic data into a CSV file
write_csv(happydb, "../output/happydb.csv")

#convert the structures of some variables
happydb$age <- as.numeric(happydb$age)
```

#Part 1: What's the difference of the words in each gender group?
*In order to analyze the components of the text in each group, the barplot and wordcloud are used.*

##Step 1 : Filter data
```{r,warning=FALSE}
female <- happydb %>%
  filter(gender == 'f') 
male <- happydb %>%
  filter(gender == 'm')

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/senselabel.csv'
sense_data <- read_csv(urlfile)

#merge the data with lower case word
# what's the most frequently used POS in the top freq words?
f_POS <- merge(freq_f,sense,by.x = 'word',by.y = 'lowercaseLemma')
f_POS <- as.matrix(table(f_POS$POS))

m_POS <- merge(freq_m,sense,by.x = 'word',by.y = 'lowercaseLemma')
m_POS <- as.matrix(table(m_POS$POS))

#combine the female data and male data
POS <- rbind(m_POS,f_POS)
POS <- data_frame(word = rownames(POS), nums= POS, gender = c(rep('male',12),rep('female',12)))
```
##Step 2: Barplot 
```{r barplot}
ggplot(POS)+
  geom_bar(aes(x = POS$word, y = POS$nums), stat="identity", fill = 'lightgreen') +
  facet_grid(~gender)+
  labs(titile = 'POS for different gender', x = 'Part of Speech', y = 'Frequency')

# most frequently used 10 words for female
ggplot(freq_f[1:10,], aes(fill = freq_f[1:10,]$word)) +
  geom_bar(aes(x = reorder(freq_f[1:10,]$word, -freq_f[1:10,]$Freq), y = freq_f[1:10,]$Freq), stat="identity", fill = 'pink')+
  labs(title='Most Frequently Used 10 Words For Female', y = 'Frequency', x = 'Words')

# most frequently used 10 words for male
ggplot(freq_m[1:10,], aes(fill = freq_m[1:10,]$word)) +
  geom_bar(aes(x = reorder(freq_m[1:10,]$word,-freq_m[1:10,]$Freq), y = freq_m[1:10,]$Freq), stat="identity", fill = 'skyblue')+
  labs(title='Most Frequently Used 10 Words For Male', y = 'Frequency', x = 'Words')
```

##Step 3: WordCloud of text word
```{r reorganize data, warning=FALSE}
female_corpus <- Corpus(VectorSource(female$text))
female_dtm <- DocumentTermMatrix(female_corpus)
freq_f <- data.frame(sort(colSums(as.matrix(female_dtm)), decreasing =TRUE))
freq_f <- data.frame(word = rownames(freq_f), Freq = freq_f[,1])

male_corpus <- Corpus(VectorSource(male$text))
male_dtm <- DocumentTermMatrix(male_corpus)
freq_m <- data.frame(sort(colSums(as.matrix(male_dtm)), decreasing =TRUE))
freq_m <- data.frame(word = rownames(freq_m), Freq = freq_m[,1])
```
```{r wordcloud}
colorVec_f = rep(c('red', 'lightpink'), length.out=nrow(freq_f))
wordcloud2(freq_f[1:100,], color = colorVec_f, fontWeight = "bold",size=0.5, shape = 'cardioid', rotateRatio = 0.2)

colorVec_m = rep(c('blue', 'skyblue'), length.out=nrow(freq_m))
wordcloud2(freq_m[1:100,], color = colorVec_m, fontWeight = "bold",size=0.5, shape = 'star', rotateRatio = 0.2)
```

##Summary
The barplots show that both male and female like use nouns, verbs and adjs to express the happy moments. The top 10 words of frequency in each groups also support the notation. Women have 8 nouns and 2 verbs and man have 7 nouns, 2 verbs and 1 adverb(finally).

In the barplot and wordcloud graphs of both female and male, we can find that both women and men are enjoyed the happy moments with their friends. But women tend to be more bond with people around them for the words like husband, daughter, son, family come up more frequently than men's. 



# Part 2: What the difference of periods in each gender group?
*For the infomation of the difference in the numbers and contents of periods in each gender group, I'm gonna use the number count, word cloud and ks-test.*

## Step 1. Numbers of reflection
```{r}
ggplot(happydb,aes(x = happydb$gender,fill = happydb$reflection_period))+
  geom_bar(position = "fill") +
  labs(title = 'Reflection Period of Different Gender', x = 'Gender')
```

## Step 2. Part of Position of Reflection
```{r}
f24h_POS <- merge(freq_f24h,sense,by.x = 'word',by.y = 'lowercaseLemma')
f24h_POS <- as.matrix(table(f24h_POS$POS))

f3m_POS <- merge(freq_f3m,sense,by.x = 'word',by.y = 'lowercaseLemma')
f3m_POS <- as.matrix(table(f3m_POS$POS))

m24h_POS <- merge(freq_m24h,sense,by.x = 'word',by.y = 'lowercaseLemma')
m24h_POS <- as.matrix(table(m24h_POS$POS))
m3m_POS <- merge(freq_m3m,sense,by.x = 'word',by.y = 'lowercaseLemma')
m3m_POS <- as.matrix(table(m3m_POS$POS))

#combine the female data and male data
f.POS <- cbind(f24h_POS,f3m_POS)
f.POS <- data_frame(word = rownames(f.POS), nums= f.POS, period = c(rep('24h',12),rep('3m',12)))

m.POS <- cbind(m24h_POS,m3m_POS)
m.POS <- data_frame(word = rownames(m.POS), nums= m.POS, period = c(rep('24h',12),rep('3m',12)))

#use the ks.test
ks.test(f.POS[,1],f.POS[,2]);ks.test(m.POS[,1],m.POS[,2])
```

## Step 3. Words of Reflection
```{r}
# filter all the data set
female_24h <- female %>%
  filter(reflection_period == 'hours_24') # female & 24h
male_24h <- male %>%
  filter(reflection_period == 'hours_24') # male & 24h
female_3m <- female %>%
  filter(reflection_period == 'months_3') # female & 3m
male_3m <- male %>%
  filter(reflection_period == 'months_3') # male & 3m
```
```{r}
# 24h happy moments of female
f24h_corpus <- Corpus(VectorSource(female_24h$text))
f24h_dtm <- DocumentTermMatrix(f24h_corpus)
freq_f24h <- data.frame(sort(colSums(as.matrix(f24h_dtm)), decreasing =TRUE))
freq_f24h <- data.frame(word = rownames(freq_f24h), Freq = freq_f24h[,1])
colorVec1 <- rep(c('palevioletred', 'hotpink'), length.out=nrow(freq_f24h))
wordcloud2(freq_f24h[3:100,], color = colorVec1, fontWeight = "bold",size=0.5, rotateRatio = 0.2)  
# 3m happy moments of female
f3m_corpus <- Corpus(VectorSource(female_3m$text))
f3m_dtm <- DocumentTermMatrix(f3m_corpus)
freq_f3m <- data.frame(sort(colSums(as.matrix(f3m_dtm)), decreasing =TRUE))
freq_f3m <- data.frame(word = rownames(freq_f3m), Freq = freq_f3m[,1])
colorVec2 <- rep(c('palevioletred', 'hotpink'), length.out=nrow(freq_f3m))
wordcloud2(freq_f3m[3:100,], color = colorVec2, fontWeight = "bold",size=0.5, rotateRatio = 0.2)
# 24h happy moments of male
m24h_corpus <- Corpus(VectorSource(male_24h$text))
m24h_dtm <- DocumentTermMatrix(m24h_corpus)
freq_m24h <- data.frame(sort(colSums(as.matrix(m24h_dtm)), decreasing =TRUE))
freq_m24h <- data.frame(word = rownames(freq_m24h), Freq = freq_m24h[,1])
colorVec3 <- rep(c('cornflowerblue','skyblue'), length.out=nrow(freq_m24h))
wordcloud2(freq_m24h[3:100,], color = colorVec3, fontWeight = "bold",size=0.5, rotateRatio = 0.2)  
# 3m happy moments of male
m3m_corpus <- Corpus(VectorSource(male_3m$text))
m3m_dtm <- DocumentTermMatrix(m3m_corpus)
freq_m3m <- data.frame(sort(colSums(as.matrix(m3m_dtm)), decreasing =TRUE))
freq_m3m <- data.frame(word = rownames(freq_m3m), Freq = freq_m3m[,1])
colorVec4 <- rep(c('cornflowerblue','skyblue'), length.out=nrow(freq_m24h))
wordcloud2(freq_m3m[3:100,], color = colorVec4, fontWeight = "bold",size=0.5, rotateRatio = 0.2)
```

##Summary 
For both female and male, there is no difference in the total number of the reflection period. But with the content of each period, female and male show differently.

Since the p-values of Kolmogorov-Smirnov test are very close to 1, the null hypothesis cannot be rejected at 0.01 significance which means there is no statistically difference between the POS of 24 hours and that of 3 months in each gender group.

After removing the most frequently used words in each group, the results show that in 24-hour's memory, women have more 'fleeting' words - words describing movement, such as watched, feel, enjoy, ect. In 3-month's memory, women have more nouns describing the person they shared the happy moments with. This is compatible with the memory loss. But focusing on men's words in different reflection period, the POS of the words seem remain.




























